---
title: "Lab 8 - Linear Regression in R"
author: "AnnaClaire Marley"
date: "11/20/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load the packages and read in the data
```{r, include = FALSE}

library(tidyverse)
library(knitr)
library(kableExtra)
library(stargazer)
library(extrafont)
salmon <- read_csv("salmon_simple.csv") %>% 
  select(year, salmon_fresh)

```

# 4. Exploratory scatterplot

```{r}
salmon_plot <- ggplot(salmon, aes(x = year, y = salmon_fresh)) +
  geom_point()
salmon_plot
```
Overall there does look like there is a linear relationship, but there are some random outliers around 2005 and 2012


# 5. Linear regression in R

```{r}

salmon_model <- lm(salmon_fresh ~ year, data = salmon)

salmon_model

```

Imports(tons) = -14982940 + 7550(Year)

y intercept means that after 1984, salmon imports are negative, which doesn't make sense


# 6. Model Diagnostics

```{r}
par(mfrow = c(2,2))
plot(salmon_model)
```
Residuals look normally distributed for the most part at first, but then become more widely spread.


# 7. Explore model fit and significance 

```{r}

summary(salmon_model)

```

- Year does significantly predict salmon imports
- R^2 is the proportion of variance in the outcome variable (y) that is explained by the predictor variable (x)
- Around 6% of salmon imports not explained by year


# 8. Prepare a final graph  

- linear regression model with the:
- original data
- model
- 95% confidence interval 

geom_smooth() means
se = TRUE means display confidence interval aorund smooth

Allison example:

```{r}
salmon_final_graph <- ggplot(salmon, aes(x = year, y = salmon_fresh)) + geom_point() +
  geom_smooth(method = lm, se = TRUE, size = 0.5, color = "gray20") + theme_bw() +
  scale_x_continuous(expand = c(0,0), limits = c(1990, 2017)) +
  labs(x = "Year", y = "U.S. Annual Fresh Salmon Imports\n(1,000 pounds)")

salmon_final_graph
```

# 9. Make predictions using the model

```{r}

new_years <- data.frame(year = c(2022, 2024, 2026, 2028))

future_predict <- predict(salmon_model, newdata = new_years, interval = "confidence") 
future_predict

# bind the prediction outcomes (column fit) with the new_years data to actually create a useful table of predicted imports and upper and lower CI

 predictions <- data.frame(new_years, future_predict) 
 predictions

```

# 10. Find Pearson's r (correlation)

```{r}

salmon_corr <- cor.test(salmon$year, salmon$salmon_fresh)
salmon_corr

```
Stron positive correlation

























